---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# humanize

[![Travis-CI Build Status](https://travis-ci.org/newtux/humanize.svg?branch=master)](https://travis-ci.org/newtux/humanize)

Humanize is an almost direct port of the python [humanize package](https://github.com/jmoiron/humanize).

The goal of humanize is to provide some utlities in order to turn values (so far times and file sizes) into human readable forms  

## Installation

You can install humanize from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("newtux/humanize")
```

## Examples

Convert times:

```{r time_example}
library(humanize)

natural_time(Sys.time())
natural_time(Sys.time() - 1)
natural_time(Sys.time() - 100)
natural_time(Sys.time() - 1000*10)
```

Works across days:

```{r}
natural_time(Sys.time() - lubridate::ddays(1))
natural_time(Sys.time() - lubridate::ddays(70))
```

And forward in time:

```{r}
natural_time(Sys.time() + lubridate::ddays(1))
```

Convert file sizes:

```{r size_example}
natural_size(300)
natural_size(3000)
natural_size(3000000)
natural_size(3000000000)
natural_size(3000000000000)
natural_size(10**26 * 30)
```


## Todo

This is still a very early cut of the package. 

- Better support in times? For diff time?
- Maybe add times relative to other times?
- Export helper functions used in tests?
- Port over the numbers code
